Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-12-15 WSSSPE3/report/wg_appendix_best_practices.tex
Update best practices appendix with POC
removing duplicate entry
accepting change and replicating to appendix

\todo{add POC here}

@@

\begin{itemize}
\item Abani Patra -- University at Buffalo
\item Sandra Gesing -- University of Notre Dame
\item Neil Chue Hong -- Software Sustainability Institute
\item Gregory Tucker -- University of Colorado at Boulder
\item Birgit Penzens -- California State University Long Beach
\item Abigail Cabunoc Mayes -- Mozilla Foundation
\item Jeff Carver -- University of Alabama
\item Frank L\"{o}ffler -- Louisiana State University 
\item Colin Venter --  University of Huddersfield
\item Lorraine Hwang -- UC Davis 
\item Sou-Cheng Choi -- NORC at the University of Chicago \&  Illinois Institute of Technology
\item Suresh Marru -- Indiana University
\item Don Middleton -- NCAR 
\item Daniel S. Katz --  University of Chicago \& Argonne National Laboratory
\item Kyle Niemeyer -- Oregon State University
\item Jeffrey Carver -- University of Alabama
\item Dan Gunter -- LBNL
\item Alexander Konovalov -- University of St Andrews
\item Tom Crick --  Cardiff Metropolitan University

@@

Core questions that will need to be explored are in knowledge management, 
(transitions between people), reliability (reproducibility), usability, and how a software tool becomes part of the core workflow of well identified users (stakeholders)
relating to tool success and hence sustainability. \katznote{prev sentence is complex and awkward} Ideas 
that may need to be explored include:
\begin{itemize}

@@

\item Dimensions of sustainability -- economic, technical, environmental,
declining interest in primary application area), \katznote{not sure what the
prev. comment goes with} social.

>>>>

Sandra Gesing\footnote{email:\href{mailto:sandra.gesing@nd.edu}{sandra.gesing@nd.edu}} will serve as
the point of contact for this working group, and be responsible for ensuring timely progress of the planned actions.

@@

\begin{itemize}
\item Abani Patra -- University at Buffalo
\item Sandra Gesing -- University of Notre Dame
\item Neil Chue Hong -- Software Sustainability Institute
\item Gregory Tucker -- University of Colorado at Boulder
\item Birgit Penzens -- California State University Long Beach
\item Abigail Cabunoc Mayes -- Mozilla Foundation
\item Frank L\"{o}ffler -- Louisiana State University 
\item Colin Venter --  University of Huddersfield
\item Lorraine Hwang -- UC Davis 
\item Sou-Cheng Choi -- NORC at the University of Chicago \&  Illinois Institute of Technology
\item Suresh Marru -- Indiana University
\item Don Middleton -- NCAR 
\item Daniel S. Katz --  University of Chicago \& Argonne National Laboratory
\item Kyle Niemeyer -- Oregon State University
\item Jeffrey Carver -- University of Alabama
\item Dan Gunter -- LBNL
\item Alexander Konovalov -- University of St Andrews
\item Tom Crick --  Cardiff Metropolitan University

@@

Core questions that will need to be explored are in reliability (reproducibility), usability, extensibility, knowledge management and continuity (transitions between people). Answers to these will guide us on how a software tool becomes part of the core workflow of well identified users (stakeholders) relating to tool success and hence sustainability.
%\katznote{prev sentence is complex and awkward} % see fix
Ideas that may need to be explored include:
\begin{itemize}

@@

\item Dimensions of sustainability -- economic, technical, environmental,
and obsolescence.
%declining interest in primary application area), \katznote{not sure what the
%prev. comment goes with} social.
